Appendix

### 2023-05-02 writing/Manuscript_2023.Rmd
updates to revision .rmd

```{r load-classifications}
# classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
#   as_tibble() %>%
#   mutate(age_numeric = age) %>%
#   mutate(age = paste('age',age,sep="")) %>%
#   mutate(age = as.factor(age)) %>%
#   mutate(category = target_label) %>% 
#   dplyr::select(-X, -X.1, -index) %>%
#   mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
#                            !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
#   mutate(site = as.factor(site)) 
```

@@

```{r join-data}
# model_classifications <- classification_data %>%
#   mutate(unique_ids = session_id) %>%
#   left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
#   left_join(tracing_by_sub)
#   
# 
# # bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
# # this was checked directly in mongodb database -- no idea why, assuming bad internet.
# tech_error_drawings <- model_classifications %>%
#   filter(is.na(num_strokes))
# # filter out tech error drawings from dataset (24)
# model_classifications <- model_classifications%>%
#   filter(!is.na(num_strokes))

@@

# humans_and_models_merged <- humans %>%
#   group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
#   summarize(prop_correct = mean(correct_or_not)) %>%
#   left_join(model_classifications, by=c('unique_ids','category')) %>% # join with classification data 
#   filter(!is.na(age))
```

@@

# human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)

@@

<!-- ### Automated recognition scores -->
<!-- We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol.  -->
<!-- To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 [@simonyan2014very], a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch [@paszke2017automatic]. -->
<!-- We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6).  -->
<!-- Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.  -->
<!-- Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing. -->
<!-- To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.  -->
<!-- No additional metadata about the age of the child who produced each sketch was provided to the model. -->
<!-- This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing. -->

@@

## Extra models after peer-review

### composite effort score
```{r}

@@

```{r}

full_model_with_effort_combined <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(effort_compiled) + 
                      (condition | unique_ids) +
                      (condition*scale(age_numeric) | category),
      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

@@

```{R}
tracing_score_by <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(effort_compiled) + 
                      (condition | unique_ids) +
                      (condition*scale(age_numeric) | category),
      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
```

@@

```{r check-drawing-time}
# drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
#                       (1 | unique_ids) +
#                       (1 | category),
#       data = d)
# drawing_time_out = summary(drawing_time)
```

@@

# xtable(full_model_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")

@@

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{rrrrr} -->
<!--   \hline -->
<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
<!--   \hline -->
<!-- Intercept & 1.39 & 0.16 & 8.51 & 0.000 \\  -->
<!--   Task & 0.02 & 0.26 & 0.08 & 0.936 \\  -->
<!--   Age & 1.16 & 0.14 & 8.59 & 0.000 \\  -->
<!--   Site & 0.60 & 0.16 & 3.71 & 0.000 \\  -->
<!--   Task*Age & -0.14 & 0.19 & -0.73 & 0.467 \\  -->
<!--   Task*Site & -0.19 & 0.16 & -1.17 & 0.244 \\  -->
<!--   Age*Site & 0.15 & 0.16 & 0.91 & 0.361 \\  -->
<!--   Task*Age*Site & 0.06 & 0.16 & 0.38 & 0.706 \\  -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}  -->
<!-- \end{table} -->

@@

# xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
```

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{rrrrr} -->
<!--   \hline -->
<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
<!--   \hline -->
<!-- Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\  -->
<!--   Task & -0.04 & 0.26 & -0.16 & 0.873 \\  -->
<!--   Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 24 -->
<!--   Site & 0.80 & 0.16 & 5.04 & 0.000 \\  -->
<!--   Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\  -->
<!--   Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\  -->
<!--   Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\  -->
<!--   Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\  -->
<!--   Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\  -->
<!--   Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\  -->
<!--   Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\  -->
<!--   Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\  -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}  -->
<!-- \end{table} -->

@@

```{r}
lmer(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site + (1|unique_ids))
```

```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals."} 
ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=.1) +
  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5, size=.3) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none", aspect.ratio=1.3) +
  geom_smooth(span = 10,alpha=smooth_alpha, aes(group =site), size=.5)  +
  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
  facet_grid(~site) +
  ylim(-.1,4.1) +
  scale_color_manual(values = natparks.pals("Acadia", 9)[c(2,8)])
  # scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)

@@

# Acknowledgements  
[BLINDED]
<!-- We thank Yi Feng and Megan Merrick for assistance with data collection. We also thank the San Jose Children's Discovery Museum for their collaboration, as well as the parents at XX and XX preschool whose children participated. Thanks to members of the Stanford Language and Cognition lab for their feedback. This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.  -->

@@

>>>>

@@

@@

@@

# human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)
```

```{r}
edu = c(17,83,298,953,202,2018)
edu_out <- edu %>%
  as_tibble() %>%
  rownames_to_column()

@@

@@

```{r}
## Extra models after peer-review
### composite effort score

@@

```{r}
full_model_with_effort_combined <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(effort_compiled) + 
                      (condition | unique_ids) +
                      (condition*scale(age_numeric) | category),
      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

@@

```{r}
# correct_by_effort_and_site <- glmer(cbind(num_correct, num_incorrect) ~ scale(draw_duration)*site + age_numeric + condition +
#                       (1 | unique_ids) +
#                       (scale(age_numeric) | category),
#       data = d,family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
# 
# correct_by_effort_and_site_out = summary(correct_by_effort_and_site)
```

```{r}
drawing_duration_by_site <- lmer(scale(draw_duration) ~ site*condition + 
                      (1 | unique_ids) +
                      (scale(age_numeric) | category),
      data = d)

drawing_duration_out = summary(drawing_duration_by_site)

papaja::apa_table(drawing_duration_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the how long children spent on each drawing as a function of site (Beijing vs. San Jose) and drawing condition.')
```
```{r}
num_strokes_by_site <- lmer(scale(num_strokes) ~ site*condition  + 
                      (1 | unique_ids) +
                      (scale(age_numeric) | category),
      data = d)

num_strokes_by_site_out = summary(num_strokes_by_site)
papaja::apa_table(num_strokes_by_site_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the number of strokes children made on each drawing as a function of site (Beijing vs. San Jose) and drawing condition.')
```

```{r}
intensity_by_site <- lmer(scale(mean_intensity) ~ site*condition  + 
                      (1 | unique_ids) +
                      (scale(age_numeric) | category),
      data = d)

intensity_by_site_out = summary(intensity_by_site)
papaja::apa_table(intensity_by_site_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the amount of "ink" (i.e., average drawing intensity) children used on each drawing as a function of site (Beijing vs. San Jose) and drawing condition.')
```

```{r}
effort_by_site <- lmer(scale(effort_compiled) ~ site*age_numeric  + 
                      (1 | unique_ids) +
                      (scale(age_numeric) | category),
      data = d)

effort_out = summary(effort_by_site)
papaja::apa_table(effort_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the amount of overall effort children used on each drawing (sum of z-scored effort covariates -- ink, strokes, and time) as a function of site (Beijing vs. San Jose) and drawing condition.')
```

```{r}
indiv_by_acc <- d %>%
  group_by(unique_ids, avg_tracing_score_scaled) %>%
  summarize(prop_correct = mean(prop_correct))

cor.test(indiv_by_acc$avg_tracing_score_scaled, indiv_by_acc$prop_correct)
```

```{r}
covariates <- d %>% select(num_strokes, draw_duration, mean_intensity, avg_tracing_score)

covariates_cor_table = round(cor(covariates),3)
rownames(covariates_cor_table)<-c('Number of strokes','Drawing duration (s)','Mean intensity','Average tracing score')
colnames(covariates_cor_table)<-c('Number of strokes','Drawing duration (s)','Mean intensity','Average tracing score')

papaja::apa_table(covariates_cor_table, caption="Pearsons corellation coefficients for all effort covariates (estimed for each drawing) and tracing scores (estimated by each participant).")

@@

```{r check-drawing-time}
drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
                      (1 | unique_ids) +
                      (1 | category),
      data = d)
drawing_time_out = summary(drawing_time)
```

@@

@@

@@

@@

```{r}
tracing_score_stats = summary((lm(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site)))

papaja::apa_table(tracing_score_stats$coefficients, caption='"Model coefficients from a  linear regression predicting the average tracing score of each child as a function of their age and the site at which they participated.')

```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals."} 
ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=.1) +
  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5, size=.5) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none", aspect.ratio=1.3) +
  geom_smooth(span = 20,alpha=smooth_alpha, aes(group =site), size=.5)  +
  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
  facet_grid(~site) +
  ylim(-.1,4.1) +
  scale_color_manual(values = natparks.pals("Acadia", 9)[c(2,8)])
  # scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)

@@

# Acknowledgements  a
[BLINDED]
<!-- We thank Yi Feng and Megan Merrick for assistance with data collection. We also thank the San Jose Children's Discovery Museum for their collaboration, as well as the parents at XX and XX preschool whose children participated. Thanks to members of the Stanford Language and Cognition lab for their feedback. This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.  -->

@@

<!-- # Appendix Table B1: drawing duration -->
<!-- # Appendix Table B2: intensity -->
<!-- # Appendix Table B3: strokes -->
<!-- # Appendix Table B4: compiled effort -->
